Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-07-18 review_article.Rmd
slight edit of Abstract

Utilising maps to present statistics has been widely used for centuries.
Connecting the data to the geographical representation of areas that are already familiar.
It is not enough to be recognisable, if the value of the statistic cannot be seen. Cancer outcomes directly relate to the people living within a geographical area. In situations where the people are of interest, not the land they live on, it is reasonable to explore views that enhance the communication of the cancer outcomes. This has spurred innovations over the previous centuries to enhance the shapes and maps presented to effectively communicate cancer outcomes.

@@

A grey literature review conducted by (ref) identified 33 Cancer Atlases publically available cancer atlases available on the internet and published between 01/01/2010 to 11/11/2015.

>>>>

Utilising maps to present statistics has been widely used for centuries.
These maps connec data and/or statistics to the geographical representation of areas that are generally familiar to the audience. However, it is not enough to be recognisable, if the meaning of the statistic cannot be seen. This is particularly relevant to cancer statistics, as cancer outcomes directly relate to the people living within a geographical area. In situations where the people are of interest, not the land they live on, it is reasonable to explore views that enhance the communication of the cancer statistics. This has spurred innovations over the previous centuries to enhance the shapes and maps presented to effectively communicate cancer outcomes, and health outcomes more braodly.

@@

A grey literature review conducted by (ref) identified 33 publically available cancer atlases published on the internet between 01/01/2010 to 11/11/2015.
